\section*{Declaration of honour} 
\addcontentsline{toc}{section}{Declaration of honour}
I hereby confirm on my honour that I personally prepared the present academic 
work and carried out myself the activities directly involved with it. I also 
confirm that I have used no resources other than those declared. All formulations 
and concepts adopted literally or in their essential content from printed, unprinted 
or Internet sources have been cited according to the rules for academic work and 
identified by means of footnotes or other precise indications of source.
\\
The support provided during the work, including significant assistance from my
supervisor has been indicated in full.
\\
The academic work has not been submitted to any other examination authority. 
The work is submitted in printed and electronic form. I confirm that the
content of the digital version is completely identical to that of the printed version.\\
\\
Date:\line(5,0){100} \hfill Signature:\line(5,0){150}
\section*{Declaration of publication}
\begin{itemize}
\item[$\square$]I hereby agree, that my thesis will be available for third party review in
purpose of academic research.
\item[$\square$]I hereby agree, that my thesis will be available after 30 years ( ยง 7 Abs. 2
BremArchivG) in the university archive for third party review in purpose
of academic research.
\item[$\square$]I hereby do not agree, that my thesis will be available for third party
review in purpose of academic research.
\end{itemize}
Datum:\line(5,0){100} \hfill Unterschrift:\line(5,0){150}